%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One-Page Professional CV
% LaTeX Template
% Version 2.0 (2021-07-02)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Modification Author:
% Vin Kumar
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
\usepackage{tabularx}
	

%\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[left=0.3in, top=0.3in, right=0.3in, bottom=0.3in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Vin Kumar} % Your name
\address{
	+1 (613) 700 - 0343 \\ 
	\href{mailto:thedualengineer@gmail.com}{thedualengineer@gmail.com}
}  % Your phone number and email
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{
	\href{https://www.linkedin.com/in/vin-kumar/}{linkedin.com/in/vin-kumar/} |
	\href{https://github.com/vkuma}{github.com/vkuma}
	|
	\href{https://noisytechnology.com}{noisytechnology.com}
}

%\address{Ottawa, Ontario, Canada}

\begin{document}

%-------------------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{University of Ottawa} {May 2021}{}

\item Bachelor of Applied Science Electrical Engineering (Co-op) and Bachelor of Science in Computing Technology
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

%------------------------------------------------

\begin{rSubsection}{PV Engineer Intern}{January 2020 - September 2020}
{\href{https://www.ciena.ca/}{Ciena}, Ottawa, ON} {} 

\item Developed a fully functioning System Admin Dashboard that allows the sys. admins to control the different services running in any particular server it was installed on. react/redux/RESTful API/MaterialUI/PHP/Apache/Linux 

\item Created and updated many test and test automation scripts that controlled a variety of proprietary software/tools.

\item Trained in creating captives of different server nodes, through fiber optics, that were used in a multitude of diagnostic tests.

\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Full Stack Engineer (Co-op)}{May 2017 - August 2017}
{\href{https://www.fr.groogitsolutions.com/}{GroogIT}, Gatineau, QC} {} 

\item Developed a fully functioning front-end as a dependent entity along with a fully functioning back-end as an independent entity (a Web App) in a 3-man team

\item Front-end, used HTML, CSS, Javascript, JQuery, PHP and used twig to render all of the HTML files

\item Back-end, created a web service using an architectural style called REST along with Symfony’s ORM component known as Doctrine

\end{rSubsection}

%------------------------------------------------


\begin{rSubsection}{Software Automation Engineer (Co-op)}{September 2016 - December 2016}{\href{https://ranovus.com/}{Ranovus}, Ottawa, ON} {} 

\item Developed an automated regression test suite to be used by design engineers to verify system functionality. Automated documentation, using the Sphinx compiling tool and ReStructuredText. Python/Pytest/Unittest/Tera Term

\item Performed QA (quality assurance) testing of new firmware/GUI releases for the optical control boards as well as maintenance. Reported all bugs through the use of Bugzilla and Jira tickets.


\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{.Net Programmer (Co-op)}{January 2016 - May 2016} {\href{https://www.tpsgc-pwgsc.gc.ca/comm/index-eng.html}{Public Services and Procurement Canada}, Ottawa, ON} {} 

\item Team 1, Maintained servers by creating a diagnostic log on its status everyday reporting, and investigating on its issues, troubleshooting them.

\item Team 2, Created a full desktop application (Java) to automate server testing and service checks.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IT Support Assistant (Co-op)}{May 2014 - August 2014}{\href{https://www.uottawa.ca/en}{University of Ottawa}, Ottawa, ON} {}

\item Provided answers to clients by identifying problems; researching answers; guiding clients through corrective steps.

\item Developed client training programs by identifying learning issues; recommending instructional language.

\end{rSubsection}
%------------------------------------------------
%------------------------------------------------
\end{rSection}

%------------------------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	ACTIVITIES STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Activites}

\begin{rSubsection}{Electrical Team Leader}{September  2017 - August 2017} {uOttawa Robotic Boat Competition} {} 
\item Delegated tasks we planned out the electrical schematics of the boat and planned a head
\item Held weekly meetings, kept tabs on progress of the team's work and the goal set while also motivating them to continuing them forward
\end{rSubsection}
\end{rSection}

%--------------------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Java, C/C++, Python, HTML/CSS/JavaScript, MATLAB, PHP, SQL, React\\ 
Knowledge of & PIC Programming, Fusion 360, Electrical/PCB/IC Design, Assembly \& Design \\
Certificates & Enhanced Security Clearance in 2016 from the Canadian Government (active)\\
		 %Strong communication skills enhancing team spirit and quality of work \\
\end{tabular}

\end{rSection}

%---------------------------------------------------------------------------------




%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%\begin{rSection}{Languages} \itemsep -1pt {}   
%\item English and Arabic (Fluent)
%
%\end{rSection}

\end{document}